Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-11 paper/manuscript.Rmd
question 4 + 5

>>>>

4) If swimming is a function of density-dependent habitat selection, what are
the costs of movement between patches? IFD assumes zero-cost movement, but could
the risk and energetic costs associated with oceanic swimming be estimated using
the potential fitness deficit that caribou are willing to tolerate before swimming to a
new island?

5) In relation to all the previous questions: how do individuals vary in their assessment of the costs and benefits of swimming between islands? Why did some caribou regularly engage in swimming events, while more than half of our marked population were never observed swimming in the ocean? The forage limitation hypothesis is generally thought to apply uniformly across populations, but individual caribou could evaluate the costs and benefits of swimming to another island differently. It is possible that some individuals, in our case ~10%, considered swimming to be less costly or perceived competition or predation more acutely than their conspecifics.
